---
title: "Demographics of Gerrymandering"
author: "Andrea Huerfano & Cory Hertog"
date: "December 8, 2017"
output: 
    slidy_presentation: default
    ioslides_presentation: default 
    
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Project Background

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## More Project Background

- Bullet 1
- Bullet 2
- Bullet 3

## Project Data: Tigris Package

```{r cars, echo = TRUE}
summary(cars)
```

## Project Data: TidyCensus Package

```{r pressure}
plot(pressure)
```



## Methods: Intersection & Area
- how we used percent area to divide populations amongs data
-image of code

## Results: Wisconsin

## Results: North Carolina

## Results: Choropleth Maps

## Areas for Improvement
-Prisons & Military Bases
-Voting Popupulation and Ciitzenship
-Coordinate systems wth 'sf' package

## Conclusion Slide
